GPU Efficient Texture Based Bezier Curve Evaluation

### 2015-08-13 Paper/paper.tex
Re-read the paper, looking decent

\teaser{
  \begin{tikzpicture}[x=5in,y=1.7in]
    \node[anchor=south west,inner sep=0] at (0,0) {\includegraphics[width=5in,height=1.7in]{Teaser.png}};
    % representative line for where the quadratic bezier curve lives in the bilinear sampled texture
    \draw[yellow,->,line width=0.5mm]    (0.41,0.25) -- (0.58,0.75);
    \draw (0.08,0.25) node[] {\Huge{A}};
    \draw (0.25,0.25) node[] {\Huge{B}};
    \draw (0.08,0.75) node[] {\Huge{B}};
    \draw (0.25,0.75) node[] {\Huge{C}};    
  \end{tikzpicture}
  \caption{\textit{Left:} 2x2 texture containing control points for a quadratic Bezier curve in each color channel. \textit{Middle:} The texture as viewed with bilinear sampling. \textit{Right:} The resulting quadratic Bezier curves when sampling along the yellow line (Alpha curve omitted).}
  \label{fig:teaser}
}

@@

%-------------------------------------------------------------------------
\section{Introduction}
\label{sec:introduction}
There are two basic ways for a shader program to have customized curve data.  One way is to evaluate the curve on the CPU at discrete intervals and put those points into a texture that can be used by the GPU.  The other way is to pass curve control point data from the CPU to the shader program as shader constants, allowing the shader program to evaluate the curve at a given $t$.

@@

\begin{figure}
  \includegraphics[width=5in]{Figure2.png}
  \caption{Quadratic Curve  \textit{Left:} Yellow is the curve calculated from shader program constants.  Red is the same curve baked out in a 4x1 texture.  \textit{Right:}  Yellow uses the technique from this paper to encode the curve in a 2x2 texture.  Red is the same curve baked out in a 4x1 texture again for comparison.}
  \label{fig:quickcomparison}
\end{figure}

@@

  \begin{figure}
    \begin{tikzpicture}[x=12.5cm,y=4.25cm]
      % border
      \draw (0cm,0cm) -- (12.5cm,0cm) -- (12.5cm,4.25cm) -- (0cm,4.25cm) -- (0cm, 0cm);   
      % raw texture, bilinear sampled texture, curve results
        \node[anchor=south west,inner sep=0] at (0.125cm,0.125cm) {\includegraphics[width=4cm,height=4cm]{Figure4Texture.png}};
        \node[anchor=south west,inner sep=0] at (4.25cm,0.125cm) {\includegraphics[width=4cm,height=4cm]{Figure4Bilinear.png}};
        \node[anchor=south west,inner sep=0] at (8.375cm,0.125cm) {\includegraphics[width=4cm,height=4cm]{Figure4Curves.png}};
        % representative line for where the quadratic bezier curve lives
        \draw[yellow,->,line width=0.5mm]    (5.25cm,1.125cm) -- (7.25cm,3.125cm);    
        \draw (0.08,0.25) node[] {\Huge{A}};
        \draw (0.25,0.25) node[] {\Huge{B}};
        \draw (0.08,0.75) node[] {\Huge{B}};
        \draw (0.25,0.75) node[] {\Huge{C}};            
    \end{tikzpicture}
    \caption{\textit{Left:} a 2x2 texture storing control points for a quadratic Bezier curve in each color channel.  \textit{Middle:} The same texture as viewed when using bilinear texture sampling.  The yellow line indicates where texture samples are taken from to evaluate the quadratic Bezier curve. \textit{Right:} The curves resulting from sampling along the yellow line (Alpha curve omitted).}   
    \label{fig:texbilcurve}
  \end{figure}

@@

This pattern continues for trilinear interpolation mapping to a cubic curve, and beyond.  $N$ dimensional linear texture sampling is just the linear interpolation between two linear texture samples of dimension $N-1$.  Bezier curves of degree $N$ are just the linear interpolation between two Bezier curves of degree $N-1$.

@@

For instance, if you had a 2x2 texture, you could encode the control points $P_0,P_1,P_2$ into the red channel, and the control points $P_1,P_2,P_3$ into the green channel.  Then, after you did a texture read, you could do a lerp between the red and the green channel values.  Since the red and green channel each contain a quadratic curve, the result would be a cubic curve, defined by the control points $P_0,P_1,P_2,P_3$  However, you've used up two of the channels for a single curve, so are getting fewer curves per texture read, but they are higher degree.  The blue and the alpha channel could either be quadratic curves, or could also be encoded such that they could be combined together to provide another cubic curve.

@@

    \caption{Rational Bezier spline vs glsl sin() function.  Sin() values in grey on top of the Bezier spline in red.  Red pixels show where the values do not match. }
    \label{fig:rationalbeziersincos}
  \end{figure}

@@

Just as b-splines can be converted into piecewise Bezier curves, NURBS can also be converted into piecewise rational Bezier curves, again using Boehm's algorithm, which means these techniques can also apply to NURBS, if they are first preprocessed into rational Bezier curves.

>>>>

\teaser{
  \begin{tikzpicture}[x=5in,y=1.7in]
    \node[anchor=south west,inner sep=0] at (0,0) {\includegraphics[width=5in,height=1.7in]{Teaser.png}};
    % representative line for where the quadratic bezier curve lives in the bilinear sampled texture
    \draw[yellow,->,line width=0.5mm]    (0.41,0.25) -- (0.58,0.75);
    \draw (0.08,0.25) node[] {\Huge{A}};
    \draw (0.25,0.25) node[] {\Huge{B}};
    \draw (0.08,0.75) node[] {\Huge{B}};
    \draw (0.25,0.75) node[] {\Huge{C}};    
  \end{tikzpicture}
  \caption{\textit{Left:} 2x2 texture containing control points for a quadratic Bezier curve in each color channel. \textit{Middle:} The texture as viewed with bilinear sampling. \textit{Right:} The resulting quadratic Bezier curves when sampling along the yellow line.}
  \label{fig:teaser}
}

@@

%-------------------------------------------------------------------------
\section{Introduction}
\label{sec:introduction}
There are two basic ways for a shader program to access customized curve data.  One way is to evaluate the curve on the CPU at discrete intervals and put those points into a texture that can be used by the GPU.  The other way is to pass curve control point data from the CPU to the shader program as shader constants, allowing the shader program to evaluate the curve at a given $t$.

@@

\begin{figure}
  \includegraphics[width=5in]{Figure2.png}
  \caption{Quadratic Curve.  \textit{Left:} Yellow is the curve calculated from shader program constants.  Red is the same curve baked out in a 4x1 texture.  \textit{Right:}  Yellow uses the technique from this paper to encode the curve in a 2x2 texture.  Red is the same curve baked out in a 4x1 texture again for comparison.}
  \label{fig:quickcomparison}
\end{figure}

@@

  \begin{figure}
    \begin{tikzpicture}[x=12.5cm,y=4.25cm]
      % border
      \draw (0cm,0cm) -- (12.5cm,0cm) -- (12.5cm,4.25cm) -- (0cm,4.25cm) -- (0cm, 0cm);   
      % raw texture, bilinear sampled texture, curve results
        \node[anchor=south west,inner sep=0] at (0.125cm,0.125cm) {\includegraphics[width=4cm,height=4cm]{Figure4Texture.png}};
        \node[anchor=south west,inner sep=0] at (4.25cm,0.125cm) {\includegraphics[width=4cm,height=4cm]{Figure4Bilinear.png}};
        \node[anchor=south west,inner sep=0] at (8.375cm,0.125cm) {\includegraphics[width=4cm,height=4cm]{Figure4Curves.png}};
        % representative line for where the quadratic bezier curve lives
        \draw[yellow,->,line width=0.5mm]    (5.25cm,1.125cm) -- (7.25cm,3.125cm);    
        \draw (0.08,0.25) node[] {\Huge{A}};
        \draw (0.25,0.25) node[] {\Huge{B}};
        \draw (0.08,0.75) node[] {\Huge{B}};
        \draw (0.25,0.75) node[] {\Huge{C}};            
    \end{tikzpicture}
    \caption{\textit{Left:} a 2x2 texture storing control points for a quadratic Bezier curve in each color channel.  \textit{Middle:} The same texture as viewed when using bilinear texture sampling.  The yellow line indicates where texture samples are taken from to evaluate the quadratic Bezier curve. \textit{Right:} The curves resulting from sampling along the yellow line.}   
    \label{fig:texbilcurve}
  \end{figure}

@@

This pattern continues for trilinear interpolation mapping to a cubic curve, and beyond.  $N$ dimensional linear texture sampling is just the linear interpolation between two linear texture samples of dimension $N-1$.  Bezier curves of degree $N$ are just the linear interpolation between two Bezier curves of degree $N-1$.  These operations are equivalent.

@@

For instance, if you had a 2x2 texture, you could encode the control points $P_0,P_1,P_2$ into the red channel, and the control points $P_1,P_2,P_3$ into the green channel.  Then, after you did a texture read, you could do a lerp between the red and the green channel values by $t$.  Since the red and green channel each contain a quadratic curve, the result would be a cubic curve, defined by the control points $P_0,P_1,P_2,P_3$  However, you've used up two of the channels for a single curve, so are getting fewer curves per texture read, but they are higher degree.  The blue and the alpha channel could either be quadratic curves, or could also be encoded such that they could be combined together to provide another cubic curve.

@@

    \caption{Rational Bezier spline vs glsl sin() function.  Sin() values in grey on top of the Bezier spline in red.  Red pixels show where the values don't match. }
    \label{fig:rationalbeziersincos}
  \end{figure}

@@

Just as b-splines can be converted into piecewise Bezier curves, NURBS can also be converted into piecewise rational Bezier curves, again using Boehm's algorithm, which means these techniques can also apply to NURBS, if they are first preprocessed into piecewise rational Bezier curves.
